Ecuador plant species GBIF

### 2023-01-12 code/L0/L0_Ecuador_plants_GBIF.Rmd
Add bdvis package for summary

# Install and load required packages
```{r}
library(rgbif)
library(mde)
library(DataExplorer)
library(summarytools)
```

@@

```{r}
# using summarytools package
dfSummary(d, 
          plain.ascii  = FALSE, 
          style        = "grid", 
          graph.magnif = 0.75, 
          valid.col    = FALSE,
          tmp.img.dir  = "/tmp")
```

>>>>

# Install and load required packages
```{r}
library(rgbif)
library(mde)
library(DataExplorer)
library(summarytools)
library(bdvis)
```

@@

```{r}
# using summarytools package
d_summary <- dfSummary(d, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(d_summary, method = "render")
view(d_summary, file = file.path(output_path,"Ecuador_BIEN_traits_summary.html"))
```

```{r}
#using bdvis package
d <- format_bdvis(d, , Latitude = "Latitude", Longitude = "Longitude", Date_collected = "Date_collected", Scientific_name = "scientificName")
bdsummary(d)
d$Date_collected <- as.Date(d$Date_collected)
bdcalendarheat(d)
chronohorogram(d)
getcellid(d, gridscale = 10)
distrigraph(d, ptype = "species")
distrigraph(d, ptype = "efforts")
distrigraph(d, ptype = "cell")
distrigraph(d, ptype = "effortspecies")
tempolar(d, timescale = "m")
bdcomplete(d)
mapgrid(d, ptype = "species", region = "Ecuador")
```
